Formalization of Network Flow Algorithms

### 2017-03-02 paper/root.tex
small typo in diagram

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,22000,25000,30000},
      ytick = {0.1,1,4,8,16},
      xticklabels = {$16k$, $19k$, $22k$, $25k$, $28k$}, 
      yticklabels = {$0.1$, $1$,$4$,$8$,$16$}, 
      smooth,
      cycle list name = black white
	]

>>>>

	\nextgroupplot[
      title={RMFGEN Networks (Goldfarb et. al)},
      title style={yshift=-2ex},
      axis x line*= bottom,
      axis y line*= left,
      xmode = log,
      ymode = log,
      xtick = {16000,19000,22000,25000,30000},
      ytick = {0.1,1,4,8,16},
      xticklabels = {$16k$, $19k$, $22k$, $25k$, $30k$}, 
      yticklabels = {$0.1$, $1$,$4$,$8$,$16$}, 
      smooth,
      cycle list name = black white
	]
